Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2021-11-29 article.rnw
Bracket (B_6)^2 for notational clarity.

Grouping was performed by constraining appropriate competition coefficients to be equal, reducing the number of free parameters in the model.
Each model fit was performed with one grouping of the interaction matrix's rows, and an independent grouping of the columns.
A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group, and such that every group contains at least one species.
Given $n$ species, there may be any integer number of groups from $1$ to $n$.
With $n$ groups, the grouping places each species into its own group, as though there were no grouping at all.
With $1$ group, every species is placed in the same group, such that all are considered to be equal in their competitive effect or response, reminiscent of the neutral model.
Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups.
The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
With six species, and the row and column groupings chosen independently, the total number of possible models is $B_6^2 = \num{\Sexpr{numbers::bell(6)^2}}$.

>>>>

Grouping was performed by constraining appropriate competition coefficients to be equal, reducing the number of free parameters in the model.
Each model fit was performed with one grouping of the interaction matrix's rows, and an independent grouping of the columns.
A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group, and such that every group contains at least one species.
Given $n$ species, there may be any integer number of groups from $1$ to $n$.
With $n$ groups, the grouping places each species into its own group, as though there were no grouping at all.
With $1$ group, every species is placed in the same group, such that all are considered to be equal in their competitive effect or response, reminiscent of the neutral model.
Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups.
The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
With six species, and the row and column groupings chosen independently, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
